Awareness and Russellian Epistemology

### 2011-01-30 foundationalism.tex
Fixed label for Hintikka section

\subsection{Jaako Hintika}\label{Russell}

@@

Hintikka's objection is reasonable.  It is counter intuitive to assume
a system of logical consequence is present at the semantic level in
epistemic logic.
However, it is not \emph{impossible}.  In the next section we sketch
an approach to epistemic logic that incorporates logical consequence
into awareness logic.  The intuition behind this move follows
Russell's formulation of \emph{acquaintance} and \emph{knowledge by
  description}.  After providing formal systems that express our
proposed reading of epistemic modality, we return Hintikka's objection
in \S\ref{hintikka-obj} in our concluding remarks.

>>>>

\subsection{Jaako Hintika}\label{Hintikka}

@@

Hintikka's objection is reasonable.  It is counter intuitive to assume
a system of logical consequence is present at the semantic level in
epistemic logic.
However, it is not \emph{impossible}.  In the next section we sketch
an approach to epistemic logic that incorporates logical consequence
into awareness logic.  The intuition behind this move follows
Russell's formulation of \emph{acquaintance} and \emph{knowledge by
  description}.  After providing formal systems that express our
proposed reading of epistemic modality, we return Hintikka's objection
in \S\ref{Hintikka} in our concluding remarks.
